Self Regulation Ontology Retest Data: Initial Exploration

### 2017-02-15 SRO_Retest_Analyses.Rmd
cont working on initial retest analyses

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
sem <- function(x) {sd(x) / sqrt(length(x))}
```

@@

```{r}
matching_dv_columns <- c()
for(i in 1:length(matching_columns)){
  if(is.numeric(matching_test_data[,matching_columns[i]]) & is.numeric(matching_test_data[,matching_columns[i]])){
    matching_dv_columns <- c(matching_dv_columns, matching_columns[i])
  }
}

@@

for(i in 1:length(matching_dv_columns)){
  cor_df[matching_dv_columns[i], 'pearson'] <- cor(matching_test_data[,matching_dv_columns[i]], matching_retest_data[,matching_dv_columns[i]], method = 'pearson', use = "pairwise.complete.obs")
  cor_df[matching_dv_columns[i], 'spearman'] <- cor(matching_test_data[,matching_dv_columns[i]],matching_retest_data[,matching_dv_columns[i]], method = 'spearman', use = "pairwise.complete.obs")
}

write.csv(cor_df,'cor_df.csv')

ggplot(cor_df, aes(pearson))+
  geom_histogram()+
  theme_bw()

ggplot(cor_df, aes(spearman))+
  geom_histogram()+
  theme_bw()
```

@@

 Rank order correlations
 Separately for tasks vs. surveys
 Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EX and HDDM; subtraction vs basic variables - single vs. multiple)
 Can you get the factor structure for the retest
 step 1:Ttest on all measures of T1 for people w and without retest
 step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2
T1 comparison for people who came back vs didn't (of all that are invited)

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
sem <- function(x) {sd(x) / sqrt(length(x))}
options(digits = 4)
```

@@

```{r}
retest_data <- as.data.frame(retest_data)
retest_subs_test_data <- as.data.frame(retest_subs_test_data)
matching_dv_columns <- c()
for(i in 1:length(matching_columns)){
  if(is.numeric(retest_data[,matching_columns[i]]) & is.numeric(retest_subs_test_data[,matching_columns[i]])){
    matching_dv_columns <- c(matching_dv_columns, matching_columns[i])
  }
}

@@

for(i in 1:length(matching_dv_columns)){
  cor_df[matching_dv_columns[i], 'pearson'] <- cor(retest_data[,matching_dv_columns[i]], retest_subs_test_data[,matching_dv_columns[i]], method = 'pearson', use = "pairwise.complete.obs")
  cor_df[matching_dv_columns[i], 'spearman'] <- cor(retest_data[,matching_dv_columns[i]],retest_subs_test_data[,matching_dv_columns[i]], method = 'spearman', use = "pairwise.complete.obs")
}
```

Distribution of Pearson correlations
```{r}
ggplot(cor_df, aes(pearson))+
  geom_histogram()+
  theme_bw()
```

Distribution of spearman correlations
```{r}
ggplot(cor_df, aes(spearman))+
  geom_histogram()+
  theme_bw()
```

Add column to tasks vs. surveys in correlation table

```{r}
cor_df$dv = row.names(cor_df)
row.names(cor_df) = seq(1:nrow(cor_df))
cor_df$task = 'task'
cor_df[grep('survey', cor_df$dv), 'task'] = 'survey'
```

Distributions of correlations by task vs. survey
```{r}
cor_df %>%
  gather(key, value, -dv, -task) %>%
  ggplot(aes(value))+
  geom_histogram()+
  theme_bw()+
  facet_wrap(key~task)
```

Rank order correlations
For tasks
```{r}
cor_df %>%
  filter(task == 'task') %>%
  select(dv, spearman, pearson) %>%
  arrange(-pearson, -spearman)
```

Mean reliability for surveys
```{r}
cor_df %>%
  filter(task == 'task') %>%
  select(dv, spearman, pearson) %>%
  arrange(-pearson, -spearman) %>%
  summarise(mean_pearson = mean(pearson),
            mean_spearman = mean(spearman))
```

For surveys

Note: Holt and Laury test-retest is pretty terrible. In previous data it was ~.35. Should check to see if there is a coding error there.
```{r}
cor_df %>%
  filter(task == 'survey') %>%
  select(dv, spearman, pearson) %>%
  arrange(-pearson, -spearman)
```

Mean reliability for surveys
```{r}
cor_df %>%
  filter(task == 'survey') %>%
  select(dv, spearman, pearson) %>%
  arrange(-pearson, -spearman) %>%
  summarise(mean_pearson = mean(pearson),
            mean_spearman = mean(spearman))
```

Drift diffusion variables: raw vars vs. EZ vs. hddm

Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EZ and HDDM; subtraction vs basic variables - single vs. multiple)
```{r}
cor_df$dv
```

@@

 Can you get the factor structure for the retest
 step 1:Ttest on all measures of T1 for people w and without retest
 step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2
T1 comparison for people who came back vs didn't (of all that are invited)
